eba_sims_data

### 2020-05-06 src/eba_sims_w_data.Rmd
cost surface functions

```{r setup, echo = FALSE}
setwd("~/eba_sims/src")
library(ggplot2)
library(gridExtra)
library(knitr)
library(dplyr)
library(plyr)
library(lubridate)
library(numbers)
library(data.table)
library(R.utils)
library(forecast)
source("pffunctions.R")
```

@@

```{r}
# Function to transfrom dates to year.week 
yearweek <- function(x = Sys.Date()) {
  xday <- ISOdate(year(x), month(x), day(x), tz=tz(x))
  dn <- 1 + (wday(x) + 5)%%7
  nth <- xday + ddays(4 - dn)
  jan1 <- ISOdate(year(nth), 1, 1, tz=tz(x))
  return(sprintf("%s.%d", format(nth, "%Y"), 1 + (nth - jan1)%/%ddays(7)))
}
```

@@

```{r}
# Check
firsts[1:20,]
```
```{r}
# Attempting vectorization of the processes below

@@

>>>>

```{r setup, echo = FALSE}
setwd("~/interval-sims/src")
library(ggplot2)
library(plotly)
library(gridExtra)
library(knitr)
library(dplyr)
library(plyr)
library(lubridate)
library(numbers)
library(data.table)
library(R.utils)
library(forecast)
source("pffunctions.R")
source("helper_functions.R")
```

@@

@@

```{r}
# Check
firsts[1:20,]
```

```{r}
# Attempting vectorization of the processes below

@@

## Cost analysis

```{r}
actual.deferral.rate <- 76565/2464190
```

```{r}
p <- 0.031
price_ratio <- 200
surface <- cost_surface(p, price_ratio)
plot_surface(surface, price_ratio, p)
plot_interactive_surface(surface)
```
